Placeholder

### 2021-02-05 Paper_Histograms.Rmd
Added template code for GLAD/EDGI prepan age graph

>>>>

##Age
###Prepan

```{r GLAD/EDGI age prepan}

GLAD.prepan %>% 
  ggplot(aes(x = age_category_collapsed)) +
  geom_bar() +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Age distribution of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "")
